---
title: "CI: object naming analysis"
# output: html_document
output: rmarkdown::github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r data import, include=FALSE}
library(cowplot)
library(plyr)
library(tidyverse)
library(here)

df_import = read_csv(here("data","01_norming","01_pilot","05_OMP-freeprod","data.csv")) %>%
  # exclude test
  # weird filter property that it will exclude NAs
  filter(is.na(comments) | comments != "TEST")
```

```{r botresponse, include=FALSE}
ggplot(df_import,aes(x=str_to_lower(botresponse))) +
  geom_histogram(stat="count")
```

```{r responses to postquestionnaire, eval=FALSE, fig.height=1.5, fig.width=4, include=FALSE}
# check responses to post questionnaire, which participants I need to exclude (e.g., HitCorrect and NativeLanguage)
df_hitcorrect = df_import %>% 
  mutate_at(vars(HitCorrect),
            funs(ifelse(HitCorrect==0,"no",
                        ifelse(HitCorrect==404,"confused","yes"))))

ggplot(df_hitcorrect,aes(x=HitCorrect)) +
  geom_bar(width = .5,
           fill = "orange") +
  xlab("did you do the hit correctly")

# languages
unique(df_import$languages)

# comments
unique(df_import$comments)
```


```{r create main data frame, message=FALSE, include=FALSE}

df_clean = df_import %>% 
  # exclude multiple submissions
  arrange(startTime) %>% 
  distinct(anon_worker_id,trial_number, .keep_all = TRUE) %>% 
  # exclude participants who didn't do the hit correctly or were confused (self reportedly)
  filter(HitCorrect==1)
  # exclude participants who are more than 2 std away from median responses
  # group_by(anon_worker_id) %>%
  # filter()

# number of participants before exclusion (20)
length(unique(df_import$anon_worker_id))
# number of participants after exclusion (20)
length(unique(df_clean$anon_worker_id))


df = df_clean %>%
  select(item,refexp,trial_number,anon_worker_id) %>% 
  rename(col_item = item)
```


### About the participants (after exclusion)

```{r subj, echo=FALSE, fig.height=6, fig.width=8, message=FALSE, warning=FALSE}
# other info
engl_spellings = c("english", "englis", "eng", "engilsh", "englsh", "en")

df_subj = df_clean %>% 
  select(age,gender,education,languages,enjoyment,timeSpent,HitCorrect,comments,anon_worker_id) %>% 
  distinct() %>% 
  mutate_at(vars(languages), funs(str_to_lower(.))) %>% 
  mutate_at(vars(languages), funs(ifelse(. %in% engl_spellings, "english", .))) %>% 
  mutate(lang=ifelse(languages == "english","english","other")) %>% 
  mutate_at(vars(age), funs(as.integer(.))) %>% 
  mutate_at(vars(enjoyment), 
            funs(ifelse(.==1,"average",
                        ifelse(.==2,"awesome","other")))) %>% 
  mutate(edu = ifelse(str_detect(education,"high_school"),"High School",
                      ifelse(str_detect(education,"college"),"College","Higher"))) %>% 
  mutate_at(vars(edu), funs(fct_relevel(.,"High School", "College", "Higher")))


mean_age = round(mean(df_subj$age),digits = 1)
p_age = ggplot(df_subj,aes(x=age)) +
  geom_bar(width = .5,
           fill = "orange") +
  geom_vline(xintercept= mean_age) +
  scale_x_continuous(breaks=c(25,50,75,mean_age))

p_gen = ggplot(df_subj,aes(x=gender)) +
  geom_bar(width = .5,
           fill = "orange")

p_edu = ggplot(df_subj,aes(x=edu)) +
  geom_bar(width = .5,
           fill = "orange") +
  xlab("education")
  # theme(axis.text.x = element_text(angle = 25, hjust = 1))

p_lang = ggplot(df_subj,aes(x=lang)) +
  geom_bar(width = .5,
           fill = "orange") +
  xlab("language")
  # theme(axis.text.x = element_text(angle=45,hjust=1))

p_enj = ggplot(df_subj,aes(x=enjoyment)) +
  geom_bar(width = .5,
           fill = "orange")

mean_time = round(mean(df_subj$timeSpent), digits = 1)
median_time = round(median(df_subj$timeSpent), digits = 1)
p_time = ggplot(df_subj,aes(x=timeSpent)) +
  geom_histogram(fill = "orange") +
  geom_vline(xintercept=mean_time) +
  geom_vline(xintercept=median_time,linetype="dashed") +
  scale_x_continuous(breaks=c(median_time,mean_time,floor(0),floor(10),floor(20),floor(30),floor(40))) +
  xlab("time spent") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

plot_grid(p_age,p_gen,p_edu,p_lang,p_enj,p_time, labels = "AUTO", ncol = 2, align = 'v')

```

## Object descriptions


```{r df prep, include=FALSE, message=FALSE}

typical_list = c(
  "green_broccoli",
	"orange_carrot",
	"white_swan",
	"yellow_banana"
)

atypical_list = c(
  "red_broccoli",
	"white_carrot",
	"green_swan",
	"orange_banana"
)

df_plot = df %>%
  # separate color and type
  separate(col_item, c("color", "item"), sep = "_", remove = FALSE) %>%
  # repair compound nouns
  mutate_at(vars(item), 
            funs(ifelse(item=="bellpepper","pepper",item))) %>% 
  # transform utterances to lower case
  mutate_at(vars(refexp),
            funs(str_to_lower(.))) %>%
  # correct misspellings
  mutate(refexp_corrected = case_when(
    refexp == "saba banana"  ~ "banana",
    (refexp == "siccors" | refexp == "scissor") ~ "scissors",
    refexp == "brocholi"  ~ "broccoli",
    refexp == "feahter"  ~ "feather",
    TRUE ~ refexp
  )) %>% 
  # repair compound nouns
  mutate_at(vars(refexp_corrected), 
            funs(str_replace_all(.,"bell pepper","pepper"))) %>% 
  # typicality categorization
  mutate(typicality = case_when(
    col_item %in% typical_list ~ "typical",
    col_item %in% atypical_list ~ "atypical",
    TRUE ~ "non-cd"
  )) %>% 
  # make columns according to utterance types
  mutate(
         # uncomment this, then color_modifier not only contains the exact 
         # color-type combination, but every refexp that contains the color
         # utt_color_modified = str_detect(refexp_corrected,color),
         utt_color_modified = refexp_corrected == paste(color,item,sep=" "),
         utt_type_only = refexp_corrected == item,
         utt_other = ifelse(!utt_color_modified & !utt_type_only, T, F)
  ) %>% 
  gather(ref_cat,ref_used,utt_color_modified,utt_type_only,utt_other) %>% 
  # change order of factor levels in ref_cat
  mutate_at(vars(ref_cat),
            funs(fct_relevel(ref_cat,"utt_type_only","utt_color_modified","utt_other"))) %>% 
  # rename factor levels in ref_cat
  mutate_at(vars(ref_cat),
            funs(mapvalues(ref_cat, 
                           from=c("utt_type_only", "utt_color_modified", "utt_other"),
                           to=c("type", "color+type", "other")))) %>%
  # change order of factor levels in typicality
  mutate_at(vars(typicality), 
            funs(fct_relevel(typicality,"typical","atypical","non-cd"))) 
```

#### Color diagnostic objects
"other" utterances: swan is often called a goose; two people identified the white carrot as parsnip

```{r cd objects, echo=FALSE, warning=FALSE, message=FALSE}

df_cd = df_plot %>% 
  filter(typicality!="non-cd") %>% 
  group_by(anon_worker_id, item) %>% 
  mutate(trial = ifelse(trial_number == min(trial_number), 1, 2)) %>% 
  ungroup() 

# df_cd %>% 
#   filter(ref_used == TRUE,
#          ref_cat == "utt_other") %>% 
#   select(col_item, refexp_corrected) %>% 
#   arrange(col_item)

# all

ggplot(df_cd,aes(x=ref_cat,
                 y=as.integer(ref_used),
                 fill=typicality)) +
  facet_wrap(vars(item)) +
  # mean
  stat_summary(fun.y = "mean",
               geom = "bar",
               position = position_dodge(width = 0.9)) +
  # error bars 
  stat_summary(fun.data = "mean_cl_boot",
               geom = "linerange",
               color = "darkgrey",
               position = position_dodge(width = 0.9)) +
  theme(axis.text.x = element_text(angle = 30, hjust = 1)) +
  scale_fill_manual(values=c("#b0d387", "#4a6d21"))
```

##### By trial analysis

The difference between typical and atypical objects decreases with the second observation of the item.


```{r cd by trial, echo=FALSE, warning=FALSE}

# first trial

first_trial = ggplot(df_cd[df_cd$trial==1,],aes(x=ref_cat,
                 y=as.integer(ref_used),
                 fill=typicality)) +
  facet_wrap(vars(item)) +
  # mean
  stat_summary(fun.y = "mean",
               geom = "bar",
               position = position_dodge(width = 0.9)) +
  # error bars 
  stat_summary(fun.data = "mean_cl_boot",
               geom = "linerange",
               color = "darkgrey",
               position = position_dodge(width = 0.9)) +
  theme(axis.text.x = element_text(angle = 30, hjust = 1)) +
  scale_fill_manual(values=c("#b0d387", "#4a6d21")) +
  theme(legend.position = "top")

# second trial

second_trial = ggplot(df_cd[df_cd$trial==2,],aes(x=ref_cat,
                 y=as.integer(ref_used),
                 fill=typicality)) +
  facet_wrap(vars(item)) +
  # mean
  stat_summary(fun.y = "mean",
               geom = "bar",
               position = position_dodge(width = 0.9)) +
  # error bars 
  stat_summary(fun.data = "mean_cl_boot",
               geom = "linerange",
               color = "darkgrey",
               position = position_dodge(width = 0.9)) +
  theme(axis.text.x = element_text(angle = 30, hjust = 1)) +
  scale_fill_manual(values=c("#b0d387", "#4a6d21")) +
  theme(legend.position = "top")

plot_grid(first_trial,second_trial, labels = "AUTO", ncol = 2, align = 'v')
```


#### Non-color diagnostic objects
"other" utterances: mug is still often called a cup; jacket is often called "coat"

```{r non-cd objects, echo=FALSE, message=FALSE, warning=FALSE}

df_noncd = df_plot %>% 
  filter(typicality=="non-cd")

# df_noncd %>% 
#   filter(ref_used == TRUE,
#          ref_cat == "utt_other") %>% 
#   select(col_item, refexp_corrected) %>% 
#   arrange(col_item)

ggplot(df_noncd,aes(x=ref_cat,
                 y=as.integer(ref_used))) +
  facet_wrap(vars(item)) +
  # mean
  stat_summary(fun.y = "mean",
               geom = "bar",
               # position = position_dodge(width = 0.9),
               fill = "#E6AB02",
               width = .5) +
  # error bars 
  stat_summary(fun.data = "mean_cl_boot",
               geom = "linerange",
               color = "darkgrey",
               position = position_dodge(width = 0.9)) +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))
  # scale_fill_manual(values=c("#b0d387", "#4a6d21"))

```















