---
title: "CI: object naming analysis"
# output: html_document
output: rmarkdown::github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r data import, include=FALSE}
library(cowplot)
# library(plyr)
library(tidyverse)
library(here)

df_import = read_csv(here("data","01_norming","02_main","03_Typicality-norming","data.csv")) %>%
  # exclude test
  # weird filter property that it will exclude NAs
  filter(is.na(comments) | comments != "TEST")
```

```{r botresponse, include=FALSE}
ggplot(df_import,aes(x=str_to_lower(botresponse))) +
  geom_histogram(stat="count")
```

```{r responses to postquestionnaire, eval=FALSE, fig.height=1.5, fig.width=4, include=FALSE}
# check responses to post questionnaire, which participants I need to exclude (e.g., HitCorrect and NativeLanguage)
df_hitcorrect = df_import %>% 
  mutate_at(vars(HitCorrect),
            funs(ifelse(HitCorrect==0,"no",
                        ifelse(HitCorrect==404,"confused","yes"))))

ggplot(df_hitcorrect,aes(x=HitCorrect)) +
  geom_bar(width = .5,
           fill = "orange") +
  xlab("did you do the hit correctly")

# languages
unique(df_import$languages)

# comments
unique(df_import$comments)
```


```{r create main data frame, message=FALSE, include=FALSE}

df_clean = df_import %>% 
  # exclude multiple submissions
  arrange(startTime) %>% 
  distinct(anon_worker_id,trial_number, .keep_all = TRUE) %>% 
  # exclude participants who didn't do the hit correctly or were confused (self reportedly)
  filter(HitCorrect==1)
  # exclude participants who are more than 2 std away from median responses
  # group_by(anon_worker_id) %>%
  # filter()

# number of participants before exclusion (20)
length(unique(df_import$anon_worker_id))
# number of participants after exclusion (18)
length(unique(df_clean$anon_worker_id))


df = df_clean %>%
  select(question,slider_val,trial_number,anon_worker_id) %>% 
  rename(col_item = question)
```


### About the participants (after exclusion)

```{r subj, echo=FALSE, fig.height=6, fig.width=8, message=FALSE, warning=FALSE}
# other info
engl_spellings = c("english", "englis", "eng", "engilsh")

df_subj = df_clean %>% 
  select(age,gender,education,languages,enjoyment,timeSpent,HitCorrect,comments,anon_worker_id) %>% 
  distinct() %>% 
  mutate_at(vars(languages), funs(str_to_lower(.))) %>% 
  mutate_at(vars(languages), funs(ifelse(. %in% engl_spellings, "english", .))) %>% 
  mutate(lang=ifelse(languages == "english","english","other")) %>% 
  mutate_at(vars(age), funs(as.integer(.))) %>% 
  mutate_at(vars(enjoyment), 
            funs(ifelse(.==1,"average",
                        ifelse(.==2,"awesome","other")))) %>% 
  mutate(edu = ifelse(str_detect(education,"high_school"),"High School",
                      ifelse(str_detect(education,"college"),"College","Higher"))) %>% 
  mutate_at(vars(edu), funs(fct_relevel(.,"High School", "College", "Higher")))


mean_age = round(mean(df_subj$age),digits = 1)
p_age = ggplot(df_subj,aes(x=age)) +
  geom_bar(width = .5,
           fill = "orange") +
  geom_vline(xintercept= mean_age) +
  scale_x_continuous(breaks=c(25,50,75,mean_age))

p_gen = ggplot(df_subj,aes(x=gender)) +
  geom_bar(width = .5,
           fill = "orange")

p_edu = ggplot(df_subj,aes(x=edu)) +
  geom_bar(width = .5,
           fill = "orange") +
  xlab("education")
  # theme(axis.text.x = element_text(angle = 25, hjust = 1))

p_lang = ggplot(df_subj,aes(x=lang)) +
  geom_bar(width = .5,
           fill = "orange") +
  xlab("language")
  # theme(axis.text.x = element_text(angle=45,hjust=1))

p_enj = ggplot(df_subj,aes(x=enjoyment)) +
  geom_bar(width = .5,
           fill = "orange")

mean_time = round(mean(df_subj$timeSpent), digits = 1)
median_time = round(median(df_subj$timeSpent), digits = 1)
p_time = ggplot(df_subj,aes(x=timeSpent)) +
  geom_histogram(fill = "orange") +
  geom_vline(xintercept=mean_time) +
  geom_vline(xintercept=median_time,linetype="dashed") +
  scale_x_continuous(breaks=c(median_time,mean_time,floor(0),floor(10),floor(25),floor(20))) +
  xlab("time spent")

plot_grid(p_age,p_gen,p_edu,p_lang,p_enj,p_time, labels = "AUTO", ncol = 2, align = 'v')

```

## Object descriptions

#### Color diagnostic objects
From the three items that were normed in two atypical colors (**carrot**, **corn**, **pumpkin**), we see the biggest difference between the red and white pumpkin. Therefore, we should choose the white pumpkin and (following from that) the green carrot and red corn.<br>
There does not seem to be a big difference between the yellow **egg** and **snowman**, but the white egg is rated even more typical and its size fits better to the other stimuli. Therefore, we should choose the egg over the snowman (given that both are also nameable).<br>
Even though the orange **banana** is predominantly rated below 50, it is still not as atypical as other objects.<br>
<br>
Means are plotted in green, medians in red.

```{r by item, include=FALSE}

cd_list = c("broccoli",
	"lettuce",
	"carrot",
	"pumpkin",
	"strawberry",
	"tomato",
	"egg",
	"snowman",
	"swan",
	"banana",
	"corn")

df_plot = df %>% 
  # separate color and type
  separate(col_item, c("color", "item"), sep = "_", remove = FALSE) %>% 
  # identify presumably color diagnostic object
  mutate(cd = ifelse(item %in% cd_list, T, F))

```

```{r typicality ratings cd, echo=FALSE, fig.height=9, fig.width=9, message=FALSE, warning=FALSE}

df_cd = df_plot %>% 
  filter(cd == T)

select_color <- function(string) {
  str_replace_all(string,"_(.)*","")
}

ggplot(df_cd, aes(x=reorder(col_item, -slider_val), y=slider_val)) +
  facet_wrap(vars(item), scale = "free_x") +
  geom_point(alpha = 0.2) +
  # error bars 
  stat_summary(fun.data = "mean_cl_boot",
               geom = "linerange",
               color = "black",
               size = 1) + 
  # median
  stat_summary(fun.y = "median",
               geom = "point",
               shape = 21,
               fill = "red",
               color = "black",
               size = 4) +
  # means
  stat_summary(fun.y = "mean",
               geom = "point",
               shape = 21,
               fill = "#7CB637",
               color = "black",
               size = 4) +
  xlab("Color") +
  ylab("Typicality slider rating") +
  scale_x_discrete(labels = select_color)

sum_file = df_cd %>%
  rename(col_type = col_item,
         type = item) %>% 
  group_by(col_type, color, type) %>% 
  summarize(typicality = median(slider_val)) %>% 
  select(col_type, color, type, typicality)
write.csv(sum_file, here("data","01_norming","02_main","typicality_data.csv"), row.names = FALSE)
```

#### Non-color diagnostic objects
Means are plotted in orange, medians in red.

```{r typicality ratings noncd, echo=FALSE, fig.height=5, fig.width=7, message=FALSE, warning=FALSE}

df_noncd = df_plot %>% 
  filter(cd == F)

ggplot(df_noncd, aes(x=reorder(item,slider_val), y=slider_val)) +
  # facet_wrap(vars(item), scale = "free_x") +
  geom_point(alpha = 0.2) +
  # error bars 
  stat_summary(fun.data = "mean_cl_boot",
               geom = "linerange",
               color = "black",
               size = 1) + 
  # median
  stat_summary(fun.y = "median",
               geom = "point",
               shape = 21,
               fill = "red",
               color = "black",
               size = 4) +
  # means
  stat_summary(fun.y = "mean",
               geom = "point",
               shape = 21,
               fill = "#E6AB02",
               color = "black",
               size = 4) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  xlab("Objects") +
  ylab("Typicality slider rating")
```

