---
title: "CI: object reference pilot analysis"
# output: html_document
output: rmarkdown::github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r data import, include=FALSE}
library(cowplot)
library(plyr)
library(tidyverse)
library(here)

df_import = read_csv(here("data","01_norming","01_pilot","08_OMP-freeprod-1shot","data.csv")) %>%
  # exclude test
  # weird filter property that it will exclude NAs
  filter(is.na(comments) | comments != "TEST")
```

```{r botresponse, include=FALSE}
ggplot(df_import,aes(x=str_to_lower(botresponse))) +
  geom_histogram(stat="count")
```

```{r responses to postquestionnaire, eval=FALSE, fig.height=1.5, fig.width=4, include=FALSE}

# languages
unique(df_import$languages)

# comments
unique(df_import$comments)
```


```{r create main data frame, message=FALSE, include=FALSE}

df_clean = df_import %>% 
  # exclude multiple submissions
  arrange(startTime) %>% 
  distinct(anon_worker_id,trial_number, .keep_all = TRUE)

# number of participants before exclusion (118)
length(unique(df_import$anon_worker_id))
# number of participants after exclusion (118)
length(unique(df_clean$anon_worker_id))


df = df_clean %>%
  select(item,refexp,trial_number,anon_worker_id) %>% 
  mutate_at(vars(item),funs(str_replace(.,"images/",""))) %>% 
  mutate_at(vars(item),funs(str_replace(.,".png",""))) %>% 
  rename(col_item = item)
  
```

## Object descriptions


```{r df prep, include=FALSE, message=FALSE}

typical_list = c(
	"orange_carrot",
	"yellow_banana"
)

atypical_list = c(
	"green_carrot",
	"orange_banana"
)

df_plot = df %>%
  # separate color and type
  separate(col_item, c("color", "item"), sep = "_", remove = FALSE) %>%
  # transform utterances to lower case
  mutate_at(vars(refexp),
            funs(str_to_lower(.))) %>%
  mutate_at(vars(refexp),
            funs(str_replace(.,"a ",""))) %>%
  # correct misspellings
  mutate(refexp_corrected = case_when(
    refexp == "banana."  ~ "banana",
    (refexp == "green carrott" | refexp == "green careta")  ~ "green carrot",
    TRUE ~ refexp
  )) %>% 
  # typicality categorization
  mutate(typicality = case_when(
    col_item %in% typical_list ~ "typical",
    col_item %in% atypical_list ~ "atypical",
    TRUE ~ "non-cd"
  )) %>% 
  # make columns according to utterance types
  mutate(
         # uncomment this, then color_modifier not only contains the exact 
         # color-type combination, but every refexp that contains the color
         # utt_color_modified = str_detect(refexp_corrected,color),
         utt_color_modified = refexp_corrected == paste(color,item,sep=" "),
         utt_type_only = refexp_corrected == item,
         utt_other = ifelse(!utt_color_modified & !utt_type_only, T, F)
  ) %>% 
  gather(ref_cat,ref_used,utt_color_modified,utt_type_only,utt_other) %>% 
  # change order of factor levels in ref_cat
  mutate_at(vars(ref_cat),
            funs(fct_relevel(ref_cat,"utt_type_only","utt_color_modified","utt_other"))) %>% 
  # rename factor levels in ref_cat
  mutate_at(vars(ref_cat),
            funs(mapvalues(ref_cat, 
                           from=c("utt_type_only", "utt_color_modified", "utt_other"),
                           to=c("type", "color+type", "other")))) %>%
  # change order of factor levels in typicality
  mutate_at(vars(typicality), 
            funs(fct_relevel(typicality,"typical","atypical","non-cd"))) 
```

#### Graph

When we compare these results to the main free production (non-1shot) study, we can observe a qualitative if not even quantitative replication. For banana, 100% of the referring expressions were type-only utterances. Here, we see a similar pattern. For carrot, almost 100% of the referring expressions for the orange carrot were type-only. This is replicated here. This pilot also replicates the higher proportion of color-type utterances in the atypical carrot case. The effect seems to be slightly bigger, but not remarkably.<br>

In conclusion, the pilot does not seem to provide essentially different results than the main production study.<br>

("other" utterances: green carrot received labels "correct" and "vegetable"; and the yellow banana was referred to with "one ripe banana")


```{r cd objects, echo=FALSE, warning=FALSE, message=FALSE}

ggplot(df_plot,aes(x=ref_cat,
                 y=as.integer(ref_used),
                 fill=typicality)) +
  facet_wrap(vars(item)) +
  # mean
  stat_summary(fun.y = "mean",
               geom = "bar",
               position = position_dodge(width = 0.9)) +
  # error bars 
  stat_summary(fun.data = "mean_cl_boot",
               geom = "linerange",
               color = "darkgrey",
               position = position_dodge(width = 0.9)) +
  theme(axis.text.x = element_text(angle = 30, hjust = 1)) +
  scale_fill_manual(values=c("#b0d387", "#4a6d21"))
```

#### Table

##### Overall
Tendency for higher color mention is there but it is driven by carrot (see next table)

```{r overview table all, echo=FALSE, warning=FALSE, message=FALSE}
# all
df_true = df_plot %>% 
  filter(ref_used)

table(df_true$typicality, df_true$ref_cat)
```

##### Carrot
Very nice difference between the typical and the atypical carrot

```{r overview table carrot, echo=FALSE, warning=FALSE, message=FALSE}
# carrot
df_carr = df_true %>% 
  filter(item=="carrot")

table(df_carr$typicality, df_carr$ref_cat)
```

##### Banana
Essentially no difference between the typical and atypical banana

```{r overview table banana, echo=FALSE, warning=FALSE, message=FALSE}
# banana
df_ban = df_true %>% 
  filter(item=="banana")

table(df_ban$typicality, df_ban$ref_cat)
```











