---
title: "CI: production pilot analysis"
# output: html_document
output: rmarkdown::github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r data import, include=FALSE}
library(cowplot)
library(plyr)
library(tidyverse)
library(here)

df_import = read_csv(here("data","02_production","01_pilot","02_mainpilot","data.csv")) %>%
  # exclude test
  # weird filter property will exclude NAs
  filter(is.na(comments) | !str_detect(comments,"TEST"))
```

# Subject pool

5 participant pairs were recruited.

```{r responses to postquestionnaire, eval=FALSE, fig.height=1.5, fig.width=4, include=FALSE}

# languages
unique(df_import$languages)

# comments
unique(df_import$comments)
```

## Exclusions

We excluded participants who indicated that they did the Hit incorrectly or were confused (7), who indicated that they had a native language other than English (4), who gave more then 20% erroneous responses (2) and who did the Hit multiple times (1). Overall, we excluded 14 people. 33 participants per condition, i.e., 66 in total, remain.

```{r participant exclusion, message=FALSE, include=FALSE}

# to identify multiple submissions
table(df_import$anon_worker_id)
# popular spellings of "english"
engl_spellings = c("english", "englis", "eng", "engilsh", "englsh", "en")

# Exclusions
df_clean = df_import %>% 
  # if native language is not english
  mutate_at(vars(languages), funs(str_to_lower(.))) %>% 
  mutate_at(vars(languages), funs(ifelse(. %in% engl_spellings, "english", .))) %>%
  filter(languages=="english") %>% 
  filter(!anon_worker_id=="826983419727052")

# number of participants before exclusion (10)
length(unique(df_import$anon_worker_id))
# number of participants after exclusion (8)
length(unique(df_clean$anon_worker_id))
```

```{r create main df, message=FALSE, include=FALSE}
# create main df
df = df_clean
```


## About the participants (after exclusion)

There are no apparent anomalies in the age and gender distributions of our participants and the general feedback was neutral to positive.
We expected that it would take participants approximately 7 minutes to complete, which seems to be reflected in the time they spent on it.

```{r subj, echo=FALSE, fig.height=6, fig.width=8, message=FALSE, warning=FALSE}

df_subj = df %>% 
  select(age,gender,timeSpent,anon_worker_id) %>% 
  distinct() %>% 
  mutate_at(vars(age), funs(as.integer(.)))

mean_age = round(mean(df_subj$age),digits = 1)
p_age = ggplot(df_subj,aes(x=age)) +
  geom_bar(width = .5,
           fill = "orange",
           color = "black") +
  geom_vline(xintercept= mean_age) +
  scale_x_continuous(breaks=c(20,30,50,60,70,mean_age))

p_gen = ggplot(df_subj,aes(x=gender)) +
  geom_bar(width = .5,
           fill = "orange",
           color = "black")

mean_time = round(mean(df_subj$timeSpent), digits = 1)
median_time = round(median(df_subj$timeSpent), digits = 1)
p_time = ggplot(df_subj,aes(x=timeSpent)) +
  geom_histogram(fill = "orange",
           color = "black") +
  geom_vline(xintercept=mean_time) +
  geom_vline(xintercept=median_time,linetype="dashed") +
  scale_x_continuous(breaks=c(median_time,mean_time,floor(5),floor(15),floor(20))) +
  xlab("time spent") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

plot_grid(p_age, p_gen, p_time, labels = "AUTO", ncol = 2, align = 'v')

```


# Main Trials

## Recap: Typicality ratings for stimuli

These are the stimuli used as targets and distractors in the study. They were normed according to their nameability and typicality in previous norming studies. We refer to objects with typicality ratings above 50 as *typical*ly colored and below 50 as *atypical*ly colored objects. The colors of the objects between the two categories are counterbalanced, i.e., there as many typical red things as there are atypical red things.

```{r import typicality data, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

typ_data = read_csv(here("data","01_norming","02_main","typicality_data.csv")) %>% 
  filter(!(col_type=="green_corn" | col_type=="white_carrot" | type=="snowman")) %>% 
  mutate(bin_typ=ifelse(typicality>50,"typical","atypical"))

ggplot(typ_data, aes(x=reorder(col_type,typicality), y=typicality, fill=color)) +
  geom_point(size=4,
             color="black",
             shape=23) +
  scale_fill_identity() +
  theme(axis.text.x = element_text(angle = 30, hjust = 1)) +
  xlab("Item") +
  ylab("Typicality\natypical ------------------ typical")

typ_data_short = typ_data %>% 
  select(col_type, typicality)
```

```{r}
df %>% 
  filter(intended_target == "thirdDistractor", 
         # str_detect(condition, "p"),
         anon_worker_id == "772581272006273") %>%
  nrow()

df_time = df %>% 
  mutate(time = endTime - startTime) %>% 
  mutate_at(vars(time), funs(./60)) %>% 
  mutate_at(vars(time), funs(./60)) %>% 
  filter(time <= 4) %>% 
  select(speaker_chat)

```


```{r}
color = c("yellow|red|orange|white|green|::y |::r |::o |::w |::g|\\|r ")
```


```{r}

# TODO: Be careful with order effects

df_target = df %>% 
  filter(intended_target=="target",
         glb_variant==1) %>%
  select(condition, speaker_chat, trial_number, anon_worker_id) %>% 
  mutate(refexp = str_c("::",speaker_chat,"::")) %>% 
  mutate_at(vars(refexp), funs(str_to_lower(.))) %>% 
  mutate(ColorMention = ifelse(str_detect(refexp,color), 1, 0)) %>% 
  filter(!str_detect(refexp,"object")) %>% 
  filter(!str_detect(refexp,"normal|regular")) %>% 
  mutate(trial_half = ifelse(trial_number <= 30, 1, 2))
```

```{r}
ggplot(df_target, aes(x=reorder(condition, -ColorMention), y=ColorMention)) +
  facet_wrap(~trial_half) +
  # mean
  stat_summary(fun.y = "mean",
               geom = "bar",
               position = position_dodge(width = 0.9)) +
  # error bars 
  stat_summary(fun.data = "mean_cl_boot",
               geom = "linerange",
               color = "darkgrey",
               position = position_dodge(width = 0.9))
```

```{r}
# 7 utterances don't have color term: 6 are for a typical target, three of which have the modifier "normal" or "regular" instead
df_target %>% 
  filter(str_detect(condition, "p") & !ColorMention)

df_target %>% 
  filter(str_detect(condition, "p") & ColorMention)
```


```{r}
df_comp = df %>% 
  filter(intended_target=="firstDistractor",
         glb_variant==1) %>%
  select(condition, speaker_chat, trial_number, anon_worker_id) %>% 
  mutate(refexp = str_c("::",speaker_chat,"::")) %>% 
  mutate_at(vars(refexp), funs(str_to_lower(.))) %>% 
  mutate(ColorMention = ifelse(str_detect(refexp,color), 1, 0)) %>% 
  filter(!str_detect(refexp,"object")) %>% 
  filter(!str_detect(refexp,"normal|regular")) %>% 
  mutate(trial_half = ifelse(trial_number <= 30, 1, 2))
```

```{r}
ggplot(df_comp, aes(x=reorder(condition, -ColorMention), y=ColorMention)) +
  facet_wrap(~trial_half) +
  # mean
  stat_summary(fun.y = "mean",
               geom = "bar",
               position = position_dodge(width = 0.9)) +
  # error bars 
  stat_summary(fun.data = "mean_cl_boot",
               geom = "linerange",
               color = "darkgrey",
               position = position_dodge(width = 0.9))
```
